\documentclass[aps,superscriptaddress,tightenlines,nofootinbib,floatfix,longbibliography,notitlepage]{revtex4-1}
\usepackage[left=18mm,right=19mm,top=23mm,bottom=16mm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{bm}
\usepackage{comment}
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor}
\usepackage{slashed}
\usepackage[multidot]{grffile} %because multiple dots in filenames confuse latex
\usepackage[
    colorlinks=true,
    allcolors=blue
]{hyperref}

\newcommand\todo[1]{{\bf\color{red}TODO: #1}}

%%%
%%%     Incorporate Repository Information
%%%

\providecommand{\repositoryInformationSetup}{} % Fallback definition if not compiled with `make DRAFT=1`.
\repositoryInformationSetup

%%%
%%%     Include latex-base macros
%%%

\input{macros} % input rather than include so we don't create macros.aux

%%%%
%%%%    Document preparation
%%%%

\begin{document}

\title{Don't Cut Corners when Deriving L\"{u}scher's Formula}
\input{authors}




\date{\today}

\begin{abstract}
L\"{u}scher's generalized zeta functions, encountered when translating finite-volume spectra into infinite-volume phase shifts, are sums typically over a momentum whose magnitude is cut off and regularized using a spherical integral.  By exactly solving two-body quantum mechanical problems we show that the correct procedure is to formulate these functions so that they match the procedure executed when taking the continuum limit, so that in a cubic volume the entirety of the Brillouin zone is accounted for, changing the counter term.
\todo{Also we are smart in other ways.  Dispersion etc.}
\end{abstract}

\maketitle

\input{section/introduction}
\input{section/hamiltonian}
\input{section/spherical}
\input{section/cartesian}
\input{section/ere}
\input{section/dispersion}
\input{section/conclusion}

\input{section/acknowledgements}
\appendix
\section{Misc}

We can put the derivation of the counter terms etc. in appendices.

Do we want to put tables?  Make numerical data directly available?  We should be good, reproducible scientists.

\input{section/dispersion-coefficients}
\input{section/counterterm/spherical}
\input{section/counterterm/cartesian}
\input{section/counterterm/dispersion}
\input{section/two-d}

\bibliography{master}

\end{document}
