\documentclass[aps,superscriptaddress,tightenlines,nofootinbib,floatfix,longbibliography,notitlepage]{revtex4-1}
\usepackage[left=18mm,right=19mm,top=23mm,bottom=16mm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{bm,bbm}
\usepackage{comment}
\usepackage{graphicx}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{slashed}
\usepackage[multidot]{grffile} %because multiple dots in filenames confuse latex
\usepackage[
    colorlinks=true,
    allcolors=blue
]{hyperref}
\usepackage{pgfplots}

\newcommand\todo[1]{{\bf\color{red}TODO: #1}}

%%%
%%%     Incorporate Repository Information
%%%

\providecommand{\repositoryInformationSetup}{} % Fallback definition if not compiled with `make DRAFT=1`.
\repositoryInformationSetup

%%%
%%%     Include latex-base macros
%%%

\input{macros} % input rather than include so we don't create macros.aux

%%%%
%%%%    Document preparation
%%%%

\begin{document}

\title{L\"{u}scher's Formalism in 1-, 2- and 3-dimensions\\--the unitary limit on the lattice and it's caveats}
\input{authors}




\date{\today}

\begin{abstract}
Studies of strongly interacting many-fermion systems at unitarity, defined invariance under scaling, require tuning the two-fermion subsystem such that phase shifts vanish.
While Finite Volume (FV) lattice descriptions allow access to systems with large numbers of fermions, FV lattice observables need to be transported to the Infinite Volume (IV) and continuum.
Possible complications with the extrapolation procedure make it difficult to study the unitary limit in three-dimensions, while for a two-dimensional system it is currently unknown how to describe the unitary limit.
In particular, L\"{u}scher's formalism directly converts FV continuum energy levels to IV continuum phase shifts at the two-body level.
Applying L\"{u}scher's formalism can be difficult because it is not always practically and sometimes even not possible to perform a continuum limit at fixed volumes.
In this paper we concentrate on the interplay of lattice discretization and FV effects.
We describe how to tune one-, two- and three-dimensional two-fermion systems to unitarity while highlighting possible difficulties.
We find that tuning to the two-dimensional unitary limit requires a simultaneous continuum and FV extrapolation.
In the three-dimensional case discretization artifacts induce finite range interactions which can be systematically removed.
These findings may help to systematically improve lattice computations of strongly interacting many-fermion observables at unitarity in two- and three-dimensional systems.
\end{abstract}

\maketitle


\input{section/introduction}

\input{section/two-particle-scattering/effective-range-expansion}
\input{section/two-particle-scattering/hamiltonian}
\input{section/two-particle-scattering/spherical-3d}

\input{section/results/three-dimensions}
\input{section/results/dispersion-3d}
\input{section/results/two-dimensions}

\input{section/conclusion}

\input{section/acknowledgements}

\appendix
\section{Misc}

We can put the derivation of the counter terms etc. in appendices.

Do we want to put tables?  Make numerical data directly available?  We should be good, reproducible scientists.

\input{section/appendix/dispersion-coefficients}
\input{section/appendix/counterterm/spherical}
\input{section/appendix/counterterm/cartesian}
\input{section/appendix/counterterm/dispersion}
\input{section/appendix/two-d}
\input{section/appendix/continuum-extrapolation}

\bibliography{master}

\end{document}
