\section{Three Dimensions}\label{sec:3D}

In this section we describe a two fermion system with a contact interaction, considering both unitarity and, later, a finite scattering length.
We implement the Hamiltonian of this system in \eqref{p space hamiltonian} in a three-dimensional cubic box of linear size $L$ with $N$ sites and lattice spacing $\epsilon=L/N$.
At first, the interaction parameter $C(\Lambda)$ of this system is tuned in the regular way.
E.g., this parameter is matched to the ground state energy $E_0$ of the system such that $E_0$ matches the first intersection of the spherical zeta function $S^{\spherical}_3$ (evaluated using software provided by \Refs{Morningstar:2017spu,Morningstar:2hib}) with the physical phase shifts \eqref{spherical quantization}.
After the interaction parameter is tuned to machine precision, the low-lying energy levels for the fixed volume and fixed lattice spacing are extracted using numeric exact diagonalization.

The tuning procedure to intersections of the zeta function with the physical phase shifts ensures that the finite-volume effects are incorporated in the energy levels and thus the contact interaction parameter is independent of the volume length $L$.
However, the interaction strength still depends on the implementation of the kinetic operator and the lattice spacing.
Therefore the strength has to be retuned for each lattice discretization implementation.
This discretization dependence has the consequence that in order to obtain \textit{pure} finite-volume energy levels which can be used to compute physical phase shifts, each lattice energy level (besides the input ground state), has to extrapolated to the continuum first.
Only when using these continuum energy levels in \Luscher's formalism, one can expect to extract infinite volume scattering information.

In practice, it is not always possible to compute any energy level in the continuum limit before using it in the finite-volume \Luscher formalism.
We therefore present consequences of the following scenarios; to obtain physical scattering data, we
\begin{enumerate}
	\item perform a continuum limit of the spectrum before inserting it in \Luscher's zeta function,
	\item insert finite-spacing energy levels into \Luscher's zeta function, followed by a continuum limit,
	\item utilize the dispersion zeta function to simultaneously perform a continuum and infinite volume limit,
	\item subtract lattice artifacts from finite-spacing eigenvalues before inserting them in the standard zeta function.
\end{enumerate}
The results for these approaches are obtained for the following parameters
\begin{equation}
    \{ L \,[\mathrm{fm}]= 1, 2 \}
    \times \left\{ \epsilon \,[\mathrm{fm}] = \frac{1}{4}, \frac{1}{5}, \frac{1}{10}, \frac{1}{20}, \frac{1}{40}, \frac{1}{50} \right\}
    \times \{ n_s = 1, 2, 3, 4, \infty \}
    \, ,
\end{equation}
as long as $N = L / \epsilon \leq 50$.


\input{section/three-dimensions/regular-luescher}
\input{section/three-dimensions/dispersion}
